What can GitHub and Googlecode Issues tell us about Exceptions in Android?

### 2014-08-30 android-stacks.tex
study description more changes

\begin{figure} \centering \includegraphics[scale=0.8]{arch3.png}
  \caption{Android Archtecture} \label{fig:exchier} \end{figure}

@@

  \item[RQ2] \noindent\emph{Which patterns of exception (mis)-use emerge?}
Based on a set of best practices compiled in this study, the study investigates whether characteristics on exception stack traces  
can pinpoint best practices violations. Chraracteristics of exception stack traces and detected violations can reveal fragilities
 on the exception handling code, which threats the application dependability. }

@@

This set of 482 projects contained overall 32,582 issues from which 4,208 stacktraces 
were extracted. Issues on Github are different from issues on dedicated bug tracking tools such as 
Bugzilla and Jira. The most important difference is that there are no predefined fields
  (e.g. severity and priority). Instead, Github uses a more open ended tagging system, on which
repositories are offered a pre-defined set of labels, but repository owners can modify 
them at will. Therefore, an issue may have none ore an arbitrary set of labels depending 
on which repository it was created. Therefore, this study is based on the assumption 
if an stack trace information embedded in an issue, it contain relevant information
that can reveal violation to best practices - regardless the lables associated to the issue.

@@

Different from GitHub, Googlecode does not provide an API to access the information related
 to hosted projects ~\footnote{Googlecode previoulsly provided a webservice but was deacrivated in June 2013.}.
However many well used open source Android application such as K9mail, is hosted in Googlecode which stores
the issue history of this and other apps are store there ~\footnote{K9mail moved to Github but advice their users to create issues on Googlecode as a way of not loosing the issue history.}.

@@

\section{RQ1: What are the common characteristics of such stack traces?}

@@

Based on the assumption that regardless the issue type, every exception stack
trace contains relevant information concerning the exception structure of the
projects analyzed, we opted for not restricting the analysis only on defect
issues.\footnote{We conducted the same analysis on the defect issues and the top
exceptions are similar to the ones mentioned on defect issues. Due to space
limitation we limit to present the general analysis here. More detailed analysis
on the defect issues can be found at:
\url{www.dimap.ufrn.br/~roberta/android_repo_mining}}

\subsection{Characterizing the Most Common Root Exceptions}

@@

@@

\subsection{Classifying Top 100 Exceptions}

@@

\begin{table}
\centering
\begin{tabular}{ll}
 \bfseries{Method} & \bfseries{Project} & & \bfseries{Ocurrences}\\
    \hline
android.os.AsyncTask &	122 & 549  \\
android.view.LayoutInflater & 63 & 163 \\
android.support.v4.* & 100 & 512\\
\hline
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

@@

>>>>

%\begin{figure} \centering \includegraphics[scale=0.8]{arch3.png}
%  \caption{Android Archtecture} \label{fig:exchier} \end{figure}

@@

  \item[RQ2] \noindent\emph{Which patterns of exception (mis)-use emerge?}
Based on a set of best practices compiled in this study, the study investigates whether characteristics on exception stack traces  
can pinpoint best practices violations. Chraracteristics of exception stack traces and detected violations can reveal fragilities
 on the exception handling code, which threats the application dependability.

@@

This set of 482 projects contained overall 32,582 issues from which 4,208 stacktraces 
were extracted. Issues on Github are different from issues on dedicated bug tracking tools such as 
Bugzilla and Jira. The most important difference is that there are no predefined fields
  (e.g. severity and priority). Instead, Github uses a more open ended tagging system, on which
repositories are offered a pre-defined set of labels, but repository owners can modify 
them at will. Therefore, an issue may have none ore an arbitrary set of labels depending 
on which repository it was created.

Based on the assumption that regardless the issue type, every exception stack
trace contains relevant information concerning the exception structure of the
projects analyzed - and therefore can review fragilities on the exceptio related code -  
we opted for not restricting the analysis only on defect
issues.\footnote{We conducted the same analysis on the defect issues and the top
exceptions are similar to the ones mentioned on defect issues. Due to space
limitation we limit to present the general analysis here. More detailed analysis
on the defect issues can be found at:
\url{www.dimap.ufrn.br/~roberta/android_repo_mining}}

@@

Different from GitHub, Googlecode does not provide an API to access the information related
 to hosted projects \footnote{Googlecode previoulsly provided a webservice but was deacrivated in June 2013.}.
However many well used open source Android application such as K9mail, is hosted in Googlecode which stores
the issue history of this and other apps are store there ~\footnote{K9mail moved to Github but advice their users to create issues on Googlecode as a way of not loosing the issue history.}.

@@

\section{The Study Results}

@@

This section presents the results amed at answering the research 
questions presented before.

\subsection{The Most Common Root Exceptions }

@@

\subsubsection{What They can Tell us?}

@@

\subsubsection{Classifying Top 100 Exceptions}

@@

\begin{table}
\centering
\begin{tabular}{lll}
 \bfseries{Method} & \bfseries{Project} & \bfseries{Ocurrences}\\
    \hline
android.os.AsyncTask &	122 & 549  \\
android.view.LayoutInflater & 63 & 163 \\
android.support.v4.* & 100 & 512\\
\hline
  \end{tabular}
\caption{Elements tresponsible for the wrapping.}
\label{tab:wrapping01}
\end{table}

@@

RESSALTAR LIMITACAO DE QUANTIDADE DE FALSOS POSITIVOS... E QUE OS STACKS SAO REAIS...
REPRESENTAM FLUXOS REAIS.... POST MOSTERN ANALISYS OF REAL EXECUTIONS....
